### 2015-11-30 fundamentals/fcsreqs.tex
line 160 adds a note about what platform CAFCA relies on (VENSIM)

The proprietary concerns of research institutions and security constraints of
data within fuel cycle simulators often restrict access. Use of a simulator is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current simulators (e.g. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, including ORION,
and \gls{VISION}.  Even when, as in the case of the MIT \gls{CAFCA} software,
the source code is unrestricted, the platform on which it relies is often
restricted or costly.  However, \Cyclus provides fully free and open access to
all users and developers, foreign and domestic.

>>>>

The proprietary concerns of research institutions and security constraints of
data within fuel cycle simulators often restrict access. Use of a simulator is
therefore often limited to its institution of origin, necessitating effort
duplication at other institutions and thereby squandering broader human
resources. License agreements and institutional approval are required for most
current simulators (e.g. \gls{COSI}6, \gls{DANESS}, \gls{DESAE}, EVOLCODE,
FAMILY21, \gls{NFCSim})\cite{juchau_modeling_2010}, including ORION,
and \gls{VISION}.  Even when the source code is unrestricted, the platform on which it relies (e.g. VENSIM) 
is often restricted or costly. The MIT \gls{CAFCA} software, for example, 
relies on the commercially licensed VENSIM product as a platform.
\Cyclus, on the other hand, provides fully free 
and open access to all users and developers, foreign and domestic.
